Title

### 2024-05-12 paper/main.tex
Updates

\begin{abstract}
	Constructing a Directed Acyclic Graph (DAG) from observational data,
	called causal discovery, is a fundamental problem in causal inference.
	Numerous algorithms have been developed to address it. However, their
	adoption in applied disciplines has been limited, possibly due to a
	lack of confidence in these algorithms stemming from them making
	obvious mistakes, and the difficulties in choosing the right algorithm
	for specific datasets. Consequently, in applied disciplines, these
	causal Directed Acyclic Graphs (DAGs) are predominantly constructed
	manually based on domain expertise. This makes it vital to test and
	potentially modify these models against data before using them for any
	analysis. Local testing based on Conditional Independence (CI) tests and
	effect sizes have been commonly used for this purpose. However,
	one of the current limitations of this approach is that there are no
	effect sizes for mixed data. To address this, we introduce a novel
	effect size measure for mixed data based on canonical correlations.
	This effect size is a generalization of some of the effect sizes used
	in special cases to mixed variables. Moreover, to assist researchers in
	constructing DAGs manually, we use the proposed mixed data effect size
	measure to build a web-based tool that can help researchers in
	constructing, validating, and modifying their DAGs with the help of
	available data. The tool iteratively suggests modifications to DAGs
	based on correlations that are not explained/over-explained by the DAG,
	while the expert chooses the direction of the edge between those
	variables. Empirically, we show that taking a greedy approach on the
	tool's recommendations can perform comparably to causal discovery
	algorithms, provided that the expert correctly determines the direction
	of the edges in at least one out of three cases, with performance
	improving as accuracy increases.
\end{abstract}

>>>>

\begin{abstract}
	\emph{Causal Discovery} is the process of learning the causal structure
	either in form of a Directed Acyclic Graph (DAG) or a Structural
	Equation Model (SEM) from observational data. This problem has been
	extensively studied for both DAGs and SEMs.
	In the field of DAGs, many automated algorithms
	have been developed for constructing a DAG from a given dataset. However, the
	adaption of these algorithms in applied fields have been limited,
	possibly due to a lack of confidence in these algorithms stemming from
	them making obvious mistakes, and the difficulties in choosing the
	right algorithm for a given dataset. Consequently, in applied
	disciplines, these DAGs are predominantly constructed manually based on
	domain expertise. Due to being constructed by hand, it is vital that
	the fit of these models are tested against data and the models are
	potentially modified to acheive a better fit. On the other hand, in the
	field of SEMs models are typically constructed manually through an
	iterative process of assessing fit and modifying the model according to
	that. This process is commonly known as \emph{Specification Search} 
	where things like \emph{modification indices} can be used to guide this
	modification process. In the case of DAGs, although there are tests
	such as Shipley 2000 that can assess the global fit of model by
	combining the implied conditional independencies of the model, but
	there are no methods that can guide our modification process. In this
	paper, we present a simple modification process based on using a
	measure of association for these individual local CI tests and
	combining it with expert knowledge. We also present a measure of
	association based on canonical correlations for mixed data. We also
	present a graphical web-tool that can assist researchers in iteratively
	modifying and constructing their DAGs. We theoretically show that in
	the presence of an oracle, this iterative modification process is
	consistent in recovering the true DAG. Emprically, we show that this
	process performs comparably to PC and Hill-Climb Search algorithms if
	the user is able to correctly identify the direction of the edge in one
	out of three cases.
\end{abstract}
